---
title: Association of childhood obesity rates with local characteristics for Year
  6 primary school children in England
output:
  html_document: default
---

```{r setup, include=FALSE,message=FALSE,warning=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#library(rmarkdown)
output_dir <- "../output"
```

Packages
```{r message=FALSE,warning=FALSE}
#Load all packages
library(plotrix)
library(arulesViz)
#devtools::install_github("rsquaredacademy/olsrr")
library(reshape2) 
library(ggcorrplot)
library(spatialreg)
library(rgdal)
library(spgwr)
library(car)
library(caret)
library(spdep)
library(tidyr)
library(olsrr)
library(car)
library(ggplot2)
library(corrplot)
library(janitor)
library(maptools)
library(RColorBrewer)
library(classInt)
library(OpenStreetMap)
library(sp)
library(rgeos)
library(tmap)
library(tmaptools)
library(sf)
library(rgdal)
library(geojsonio)
library(openxlsx)
library(plotly)
library(tidyverse)
library(dplyr)
library(assertive)
library(plyr)
library(naniar)
```

## SECTION 1: Data management
Read in national child measurement data and convert to a data frame.
```{r message=FALSE,results=='hide',warning=FALSE}
######Read in national child measurement data and convert to a data frame.
obesitydata<-read.csv("data/yr6_childmeasurement201819.csv")
obesitydata<-data.frame(obesitydata)
childdata<-obesitydata[-grep("^E1",obesitydata[,2]),]
childdata<- childdata %>% dplyr::filter(!(ONS.Code==""))
```

Rename LA variable and more data cleasning.

```{r message=FALSE,warning=FALSE}
#Rename LA variable
names(childdata)[1] <- c("LA")
childdata<- childdata %>% dplyr::filter(!(LA=="ENGLAND1"))
class(childdata)
#check dataset
names(childdata)
summary(childdata)
#Rename ons code variable
names(childdata)[2] <- c("2011GSS_CODE")



#Keep obesity related variables to reduce size of file.
childdata<- childdata[,c( "LA","2011GSS_CODE","Obese_percent","overandobese_percent", "Severely.obese_percent", "Total.number.of.children")]    
#Change variables into numeric variables
childdata$Obese_percent_num <- as.numeric(childdata$"Obese_percent")
str(childdata)

childdata$Severely.obese_percent<- revalue(childdata$"Severely.obese_percent", c("x"="0"))
childdata$Severely.obese_percentnum <-as.numeric(paste((childdata$"Severely.obese_percent")))
#Create obesity rate variable.
childdata$obesity_rate<- childdata$Obese_percent_num +childdata$Severely.obese_percentnum
childdata<- childdata[,c( "LA","2011GSS_CODE","Obese_percent","overandobese_percent", "obesity_rate", "Total.number.of.children")]   


#NCMP data uses 2011 LA ecode, LA code changed for 2019, need to add in new code to allow IMD variables to be fully merged.
childdata$GSS_CODE<- (childdata$"2011GSS_CODE")
#New 2019 code: E06000058 - Bournemouth, Christchurch and Poole - new unitary authority instead of:
#Old code:E06000028	Bournemouth,E06000029	Poole,E07000048	Christchurch
childdata$GSS_CODE<- revalue(childdata$"GSS_CODE", c("E06000028"="E06000058","E06000029"="E06000058","E07000048"="E06000058"))

#New 2019 code:E06000059 - Dorset - new unitary authority - (Dorset county abolished)
#Old code:E07000049	East Dorset,E07000050	North Dorset,E07000051	Purbeck,E07000052	West Dorset,E07000053	Weymouth and Portland
childdata$GSS_CODE<- revalue(childdata$"GSS_CODE", c("E07000049"="E06000059","E07000050"="E06000059","E07000051"="E06000059",
                                                     "E07000052"="E06000059","E07000053"="E06000059"))


#New 2019 code:E07000244 - East Suffolk - new local authority district (Suffolk Coastal and Waveney districts abolished)
#Old code:E07000205	Suffolk Coastal,E07000206	Waveney
childdata$GSS_CODE<- revalue(childdata$"GSS_CODE", c("E07000205"="E07000244","E07000206"="E07000244"))


#New 2019 code:E07000245 - West Suffolk - new local authority district (Forest Heath and St Edmundsbury districts abolished)
#Old code:E07000201	Forest Heath,E07000204	St. Edmundsbury
childdata$GSS_CODE<- revalue(childdata$"GSS_CODE", c("E07000201"="E07000245","E07000204"="E07000245"))

#New 2019 code:E07000246 - Somerset West and Taunton - new local authority district (Taunton Deane and West Somerset districts abolished)
#Old code:E07000190	Taunton Deane,E07000191	West Somerset
childdata$GSS_CODE<- revalue(childdata$"GSS_CODE", c("E07000190"="E07000246","E07000191"="E07000246"))

#####Fast food shop density file
fastfood<-read.csv("data/fastfood_outlet.csv")
fastfood<-data.frame(fastfood)
is.na(fastfood) <- fastfood == "*"
fastfood$fast_food_density<-as.numeric(paste((fastfood$"Rate.per.100.000.population")))
#La code for this data is for 2018, change some of the codes to 2011 La code to allow full merge into main data.
#change E06000048	Northumberland to	E06000057
#change E07000097	East Hertfordshire	to	E07000242
#change E07000100	St Albans	to	E07000240
#change E07000101	Stevenage	to	E07000243
#change E07000104	Welwyn Hatfield	to	E07000241
#change E08000020	Gateshead	to	E08000037
fastfood$LA.code<- revalue(fastfood$"LA.code", c("E06000048"="E06000057"))
fastfood$LA.code<- revalue(fastfood$"LA.code", c("E07000097"="E07000242"))
fastfood$LA.code<- revalue(fastfood$"LA.code", c("E07000100"="E07000240"))
fastfood$LA.code<- revalue(fastfood$"LA.code", c("E07000101"="E07000243"))
fastfood$LA.code<- revalue(fastfood$"LA.code", c("E07000104"="E07000241"))
fastfood$LA.code<- revalue(fastfood$"LA.code", c("E08000020"="E08000037"))
names(fastfood)[2] <- c("2011GSS_CODE")
#Merge into main data.
childdata <- merge(x = childdata, y = fastfood, by = "2011GSS_CODE", all.x = TRUE)

#####Ethnicity data uses the 2011 ecode as well, merge in ethnicity data first.
ethnicity<-read.csv("data/census_ethnicity.csv")
ethnicity<-data.frame(ethnicity)
names(ethnicity)[3] <- c("2011GSS_CODE")
#Only keep variables of interest to reduce size of data.
ethnicity_por<- ethnicity[,c("2011GSS_CODE","Sex..All.persons..Age..Age.0.to.24..Ethnic.Group..All.categories..Ethnic.group..measures..Value",
                             "Sex..All.persons..Age..Age.0.to.24..Ethnic.Group..White..Total..measures..Value", 
                             "Sex..All.persons..Age..Age.0.to.24..Ethnic.Group..Mixed.multiple.ethnic.group..Total..measures..Value",
                             "Sex..All.persons..Age..Age.0.to.24..Ethnic.Group..Asian.Asian.British..Total..measures..Value",
                             "Sex..All.persons..Age..Age.0.to.24..Ethnic.Group..Black.African.Caribbean.Black.British..Total..measures..Value",
                             "Sex..All.persons..Age..Age.0.to.24..Ethnic.Group..Other.ethnic.group..Total..measures..Value")]


#Merge with main dataset
childdata2 <- merge(x = childdata, y = ethnicity_por, by = "2011GSS_CODE", all.x = TRUE)


#Summarise the ethnicity and obesity data for the unitary local authorites that were combined in 2019.
childdata2 <-data.frame(aggregate(. ~ GSS_CODE,childdata2, sum))

#Create percentage variables for each ethnic group.
childdata2$percent_white<- childdata2[[ "Sex..All.persons..Age..Age.0.to.24..Ethnic.Group..White..Total..measures..Value"]]/childdata2[["Sex..All.persons..Age..Age.0.to.24..Ethnic.Group..All.categories..Ethnic.group..measures..Value"]]
childdata2$percent_mix<- childdata2[["Sex..All.persons..Age..Age.0.to.24..Ethnic.Group..Mixed.multiple.ethnic.group..Total..measures..Value"]]/childdata2[["Sex..All.persons..Age..Age.0.to.24..Ethnic.Group..All.categories..Ethnic.group..measures..Value"]]
childdata2$percent_asian<- childdata2[["Sex..All.persons..Age..Age.0.to.24..Ethnic.Group..Asian.Asian.British..Total..measures..Value"]]/childdata2[["Sex..All.persons..Age..Age.0.to.24..Ethnic.Group..All.categories..Ethnic.group..measures..Value"]]
childdata2$percent_african<- childdata2[[ "Sex..All.persons..Age..Age.0.to.24..Ethnic.Group..Black.African.Caribbean.Black.British..Total..measures..Value"]]/childdata2[["Sex..All.persons..Age..Age.0.to.24..Ethnic.Group..All.categories..Ethnic.group..measures..Value"]]




#New 2019 code: E06000058 - Bournemouth, Christchurch and Poole - new unitary authority instead of:
#Old code:E06000028	Bournemouth,E06000029	Poole,E07000048	Christchurch

childdata2$obesity_rate<- with(childdata2, ifelse(GSS_CODE=='E06000058',(childdata2$obesity_rate)/3,obesity_rate))
childdata2$fast_food_density<- with(childdata2, ifelse(GSS_CODE=='E06000058',(childdata2$fast_food_density)/3,fast_food_density))

#New 2019 code:E06000059 - Dorset - new unitary authority - (Dorset county abolished)
#Old code:E07000049	East Dorset,E07000050	North Dorset,E07000051	Purbeck,E07000052	West Dorset,E07000053	Weymouth and Portland

childdata2$obesity_rate<- with(childdata2, ifelse(GSS_CODE=='E06000059',(childdata2$obesity_rate)/5,obesity_rate))
childdata2$fast_food_density<- with(childdata2, ifelse(GSS_CODE=='E06000059',(childdata2$fast_food_density)/5,fast_food_density))
#New 2019 code:E07000244 - East Suffolk - new local authority district (Suffolk Coastal and Waveney districts abolished)
#Old code:E07000205	Suffolk Coastal,E07000206	Waveney
childdata2$obesity_rate<- with(childdata2, ifelse(GSS_CODE=='E07000244',(childdata2$obesity_rate)/2,obesity_rate))
childdata2$fast_food_density<- with(childdata2, ifelse(GSS_CODE=='E07000244',(childdata2$fast_food_density)/2,fast_food_density))
#New 2019 code:E07000245 - West Suffolk - new local authority district (Forest Heath and St Edmundsbury districts abolished)
#Old code:E07000201	Forest Heath,E07000204	St. Edmundsbury
childdata2$obesity_rate<- with(childdata2, ifelse(GSS_CODE=='E07000245',(childdata2$obesity_rate)/2,obesity_rate))
childdata2$fast_food_density<- with(childdata2, ifelse(GSS_CODE=='E07000245',(childdata2$fast_food_density)/2,fast_food_density))

#New 2019 code:E07000246 - Somerset West and Taunton - new local authority district (Taunton Deane and West Somerset districts abolished)
#Old code:E07000190	Taunton Deane,E07000191	West Somerset
childdata2$obesity_rate<- with(childdata2, ifelse(GSS_CODE=='E07000246',(childdata2$obesity_rate)/2,obesity_rate))
childdata2$fast_food_density<- with(childdata2, ifelse(GSS_CODE=='E07000246',(childdata2$fast_food_density)/2,fast_food_density))

######Read in multiple excel tabs for the imd data.

IMD_income <- read.xlsx('data/IMD2019.xlsx',sheet=3)
IMD_employ <- read.xlsx('data/IMD2019.xlsx',sheet=4)
IMD_edu <- read.xlsx('data/IMD2019.xlsx',sheet=5)
IMD_health <- read.xlsx('data/IMD2019.xlsx',sheet=6)
IMD_crime <- read.xlsx('data/IMD2019.xlsx',sheet=7)
IMD_barriers <- read.xlsx('data/IMD2019.xlsx',sheet=8)
IMD_living <- read.xlsx('data/IMD2019.xlsx',sheet=9)
IMD_idaci <- read.xlsx('data/IMD2019.xlsx',sheet=10)
#Put data into data frames.

IMD_income <- data.frame(IMD_income)
IMD_employ <- data.frame(IMD_employ)
IMD_edu <- data.frame(IMD_edu)
IMD_health <- data.frame(IMD_health)
IMD_crime <- data.frame(IMD_crime)
IMD_barriers <- data.frame(IMD_barriers)
IMD_living <- data.frame(IMD_living)
IMD_idaci <- data.frame(IMD_idaci)

#Rename ons code variable
names(childdata)[2] <- c("GSS_CODE")
names(IMD_income)[1] <- c("GSS_CODE")
names(IMD_employ)[1] <- c("GSS_CODE")
names(IMD_edu)[1] <- c("GSS_CODE")
names(IMD_health)[1] <- c("GSS_CODE")
names(IMD_crime)[1] <- c("GSS_CODE")
names(IMD_barriers)[1] <- c("GSS_CODE")
names(IMD_living)[1] <- c("GSS_CODE")
names(IMD_idaci)[1] <- c("GSS_CODE")
#Remove duplicate variables in these files.
IMD_income <-within(IMD_income, rm("Local.Authority.District.name..2019."))
IMD_employ <-within(IMD_employ , rm("Local.Authority.District.name..2019."))
IMD_edu <-within(IMD_edu, rm("Local.Authority.District.name..2019."))
IMD_health <-within(IMD_health, rm("Local.Authority.District.name..2019."))
IMD_crime <-within(IMD_crime, rm("Local.Authority.District.name..2019."))
IMD_barriers <-within(IMD_barriers, rm("Local.Authority.District.name..2019."))
IMD_living <-within(IMD_living, rm("Local.Authority.District.name..2019."))
IMD_idaci <-within(IMD_idaci, rm("Local.Authority.District.name..2019."))




#Merge the datasets
childdata2 <- merge(x = childdata2, y = IMD_income, by = "GSS_CODE", all.x = TRUE)
childdata2 <- merge(x = childdata2, y = IMD_employ, by = "GSS_CODE", all.x = TRUE)
childdata2 <- merge(x = childdata2, y = IMD_edu, by = "GSS_CODE", all.x = TRUE)
childdata2 <- merge(x = childdata2, y = IMD_health, by = "GSS_CODE", all.x = TRUE)
childdata2 <- merge(x = childdata2, y = IMD_crime, by = "GSS_CODE", all.x = TRUE)
childdata2 <- merge(x = childdata2, y = IMD_barriers, by = "GSS_CODE", all.x = TRUE)
childdata2 <- merge(x = childdata2, y = IMD_living, by = "GSS_CODE", all.x = TRUE)
childdata2 <- merge(x = childdata2, y = IMD_idaci, by = "GSS_CODE", all.x = TRUE)



#Physical activity data
activity <- read.xlsx('data/childactivity.xlsx',sheet=1)
activity<-data.frame(activity)
exercise<- activity[,c("La","GSS_CODE","X60minplus_Rate....","fairly_active_Rate....","Less_active_Rate....")]
is.na(exercise) <- exercise == "^"
is.na(exercise) <- exercise == "*"
exercise$active_rate <-as.numeric(paste((exercise$"X60minplus_Rate....")))
exercise$fairly_active_rate <-as.numeric(paste((exercise$"fairly_active_Rate....")))
exercise$less_active_rate <-as.numeric(paste((exercise$"Less_active_Rate....")))
exercise<- exercise[,c("La","GSS_CODE","active_rate", "fairly_active_rate","less_active_rate")]
#Merge with main dataset
childdata2 <- merge(x = childdata2, y =exercise, by = "GSS_CODE", all.x = TRUE)

#Keep only relavent IMD variables. We will use the score variables.
childdata2<- childdata2[,c("GSS_CODE","obesity_rate","fast_food_density","active_rate",
                           "percent_white",                                                                                  
                           "percent_mix",                                                                                   
                           "percent_asian",                                                                                  
                           "percent_african",
                           "Income...Average.rank",
                           "Employment...Average.rank",
                           "Education..Skills.and.Training...Average.rank",
                           "Health.Deprivation.and.Disability...Average.rank",
                           "Crime...Average.rank",
                           "Barriers.to.Housing.and.Services...Average.rank",
                           "Living.Environment...Average.rank",
                           "IDACI...Average.rank",
                           "Income...Average.score",
                           "Employment...Average.score",
                           "Education..Skills.and.Training...Average.score",
                           "Health.Deprivation.and.Disability...Average.score",
                           "Crime...Average.score",
                           "Barriers.to.Housing.and.Services...Average.score",
                           "Living.Environment...Average.score",
                           "IDACI...Average.score",
                           "fairly_active_rate","less_active_rate" )]
names(childdata2)
#Rename variables with clearer names.


names(childdata2)[3] <- "Density of fast food outlets"
names(childdata2)[4] <- "Active rate"
names(childdata2)[5] <- "Percentage of White children"
names(childdata2)[6] <- "Percentage of Mixed children"
names(childdata2)[7] <- "Percentage of Asian children"
names(childdata2)[8] <- "Percentage of African children"
names(childdata2)[17] <- "IMD income average score"
names(childdata2)[18] <- "IMD employment average score"
names(childdata2)[19] <- "IMD education average score"
names(childdata2)[20] <- "IMD health average score"
names(childdata2)[21] <- "IMD crime average score"
names(childdata2)[22] <- "IMD housing average score"
names(childdata2)[23] <- "IMD living average score"
names(childdata2)[24] <- "IMD IDACI average score"
names(childdata2)[25] <- "Fairly active rate"
names(childdata2)[26] <- "Less active rate"

```
## SECTION 2: Regression analysis

Check dependent variable is normal.Appendix Figure A1
```{r warning=FALSE}
#Check dependent variable is normal.
boxplot(childdata2$obesity_rate,main="Boxplot of obesity rate")
```

Check transformations of dependent variable and see which one will be normal.
Appendix Figure A1
```{r warning=FALSE}
#Check transformations of dependent variable and see which one will be normal.
symbox(~`obesity_rate`, childdata2, na.rm=T, powers=seq(-3,3,by=.5),main="Types of transformation",ylab="Obesity rate", xlab="Power of transformation")
```


```{r warning=FALSE}
#Based on this, use square root instead.
childdata2$root_ob<- sqrt(childdata2$obesity_rate)
boxplot(childdata2$root_ob,main="Boxplot of transformed obesity rate")
```


```{r include=FALSE,message=FALSE,warning=FALSE}
#Read in Shapefile.

EW <- geojsonio::geojson_read("https://opendata.arcgis.com/datasets/c7ccadc7024c4df58f9dfdc07c9acab5_0.geojson", what = "sp")

ENGLANDMapSF <- st_as_sf(EW)

ENGLANDMapSF<- st_transform(ENGLANDMapSF, 27700)
names(ENGLANDMapSF)[2] <- c("GSS_CODE")
```

Join main dataset and map data

```{r include=FALSE,message=FALSE,warning=FALSE}
#Join main dataset and map data

ObesityMAP<-merge(ENGLANDMapSF, childdata2, by.x="GSS_CODE", by.y="GSS_CODE")
#ObesityMAP <- na.omit(ObesityMAP)

modeldata<- childdata2[,-c(2)]

```

Appendix Table 1: Univariate regression
```{r warning=FALSE}
#Variable selection.
#Univariate regression first.

model_1 <- lm(root_ob ~ `Density of fast food outlets`, data = modeldata)#significant
summary(model_1)
model_2 <- lm(root_ob ~ `Active rate`, data = modeldata)#significant
summary(model_2)
model_3 <- lm(root_ob ~ `Percentage of White children`, data = modeldata)#significant
summary(model_3)
model_4 <- lm(root_ob ~ `Percentage of Mixed children`, data = modeldata)#significant
summary(model_4)
model_5 <- lm(root_ob ~ `Percentage of Asian children`, data = modeldata)#significant
summary(model_5)
model_6 <- lm(root_ob ~ `Percentage of African children`, data = modeldata)#significant
summary(model_6)
model_7 <- lm(root_ob ~ `IMD income average score`, data = modeldata)#significant
summary(model_7)
model_8 <- lm(root_ob ~ `IMD employment average score`, data = modeldata)#significant
summary(model_8)
model_9 <- lm(root_ob ~ `IMD education average score`, data = modeldata)#significant
summary(model_9)
model_10 <- lm(root_ob ~ `IMD health average score`, data = modeldata)#significant
summary(model_10)
model_11 <- lm(root_ob ~ `IMD crime average score`, data = modeldata)#significant
summary(model_11)                                 
model_12 <- lm(root_ob ~ `IMD housing average score`, data = modeldata)#insignificant
summary(model_12)                       
model_13 <- lm(root_ob ~ `IMD living average score`, data = modeldata)#significant
summary(model_13) 
model_14 <- lm(root_ob ~ `IMD IDACI average score`, data = modeldata)#significant
summary(model_14)                           
model_15 <- lm(root_ob ~ `Fairly active rate`, data = modeldata)#insignificant
summary(model_15) 
model_16 <- lm(root_ob ~ `Less active rate`, data = modeldata)#significant
summary(model_16)
```

Check correlation of model variables.
```{r warning=FALSE,include=FALSE,message=FALSE}
regvars <- modeldata[,c("Density of fast food outlets",
                        "Percentage of White children",
                        "Percentage of Mixed children",
                        "Percentage of Asian children",
                        "Percentage of African children",
                        "IMD income average score",
                        "IMD employment average score",
                        "IMD education average score",
                        "IMD health average score",
                        "IMD crime average score",
                        "IMD living average score",
                        "IMD IDACI average score",
                        "Active rate",
                        "Less active rate")]

str(regvars)

#compute the correlation matrix for the two variables of interest
corr <- cor(regvars, use="complete.obs", method="pearson")
```

##Figure 2.
Visualise the correlation matrix
```{r warning=FALSE,message=FALSE}
#visualise the correlation matrix
ggcorrplot(corr, hc.order = TRUE, type = "lower",
           outline.col = "white",tl.cex = 11,
           colors = c("#6D9EC1", "white", "#E46726"))
```

Final model selection based on F test, adjusted R etc.

```{r warning=FALSE}
#Final model selection based on F test, adjusted R etc.
model_a <-lm(root_ob ~`Density of fast food outlets`+	`Percentage of Mixed children`+	`Percentage of Asian children`+	`Percentage of African children`+	`IMD education average score`+	`IMD health average score`+	`IMD crime average score`+`IMD living average score`+	`IMD IDACI average score`+`Less active rate`, data = modeldata)
summary(model_a)
```


```{r warning=FALSE}
#Remove less active rate
model_b <-lm(root_ob ~`Density of fast food outlets`+	`Percentage of Mixed children`+	`Percentage of Asian children`+	`Percentage of African children`+	`IMD education average score`+	`IMD health average score`+	`IMD crime average score`+`IMD living average score`+	`IMD IDACI average score`, data = modeldata)
summary(model_b)
```


```{r warning=FALSE} 
#Remove fast food shop density
model_c <-lm(root_ob ~	`Percentage of Mixed children`+	`Percentage of Asian children`+	`Percentage of African children`+	`IMD education average score`+	`IMD health average score`+	`IMD crime average score`+`IMD living average score`+	`IMD IDACI average score`, data = modeldata)
summary(model_c) 
```


```{r warning=FALSE}
#Remove living average score
model_d <-lm(root_ob ~	`Percentage of Mixed children`+	`Percentage of Asian children`+	`Percentage of African children`+	`IMD education average score`+	`IMD health average score`+	`IMD crime average score`+	`IMD IDACI average score`, data = modeldata)
summary(model_d) 
```


```{r warning=FALSE}
#Remove crime average score instead of living average score
model_e <-lm(root_ob ~	`Percentage of Mixed children`+	`Percentage of Asian children`+	`Percentage of African children`+	`IMD education average score`+	`IMD health average score`+	`IMD living average score`+	`IMD IDACI average score`, data = modeldata)
summary(model_e) 
```


```{r warning=FALSE}
#Remove crime average score and living average score
model_f <-lm(root_ob ~	`Percentage of Mixed children`+	`Percentage of Asian children`+	`Percentage of African children`+	`IMD education average score`+	`IMD health average score` +	`IMD IDACI average score`, data = modeldata)
summary(model_f)
```

Stepwise AIC and best subset variable selection (reference only).
```{r warning=FALSE}
# stepwise aic regression
#Run for all variables
ols_step_both_aic(model_a)
k <- ols_step_both_aic(model_a)
ols_step_both_aic(model_a, details = FALSE)

ols_step_best_subset(model_a)
#Run for model f
ols_step_both_aic(model_f)
k <- ols_step_both_aic(model_f)
ols_step_both_aic(model_f, details = FALSE)

ols_step_best_subset(model_f)
```


```{r warning=FALSE}
#save the residuals into dataframe
finalmodel<- lm(root_ob ~	`Percentage of Mixed children`+	`Percentage of Asian children`+	`Percentage of African children`+	`IMD education average score`+	`IMD health average score` +	`IMD IDACI average score`, data = modeldata)
summary(finalmodel) 
#Check multicollinearity
vif(finalmodel)
ObesityMAP$`Model residuals`<- finalmodel$residuals
```

Figure 3. Diagnostic plots for OLS regression model
```{r warning=FALSE}
#residual plot
par(mfrow = c(2, 2))  # Split the plotting panel into a 2 x 2 grid
plot(finalmodel)  # Plot the model residuals
```

Cross-validation of model
```{r warning=FALSE}
###Cross-validation of model
#####Cross-Validation 
set.seed(48)
regressdata<-modeldata[,c("Percentage of Mixed children","Percentage of Asian children",
                          "Percentage of African children","IMD education average score",
                          "IMD health average score","IMD IDACI average score",
                       "root_ob" )]
model<- train(root_ob ~	`Percentage of Mixed children`+	`Percentage of Asian children`+	`Percentage of African children`+	`IMD education average score`+	`IMD health average score` +	`IMD IDACI average score`,
               regressdata,
              method="lm", 
              trControl=trainControl(method="repeatedcv",
                                     number=10,
                                     verboseIter=TRUE))
summary(model)
```

#print R2, MAE and RMSE
```{r warning=FALSE}
#print R2, MAE and RMSE
print(model)
```

#Now check for spatial auto-correlation
```{r warning=FALSE}

ObesityMAP <- as(ObesityMAP,"Spatial")
```


```{r warning=FALSE}
names(ObesityMAP)
#Calculate centriod of each LA.
coordsW <- coordinates(ObesityMAP)
plot(coordsW)


#Neighbours list of queens contiguity
LWard_nb <- poly2nb(ObesityMAP, queen=T)

#and nearest neighbours
knn_wards <- knearneigh(coordsW, k=4)
LWard_knn <- knn2nb(knn_wards)

#plot and add a map
plot(LWard_nb, coordinates(coordsW), col="red")
plot(LWard_knn, coordinates(coordsW), col="blue")
plot(ObesityMAP)


#create a spatial weights matrix 
Lward.queens_weight <- nb2listw(LWard_nb, style="C",zero.policy=TRUE)
Lward.knn_4_weight <- nb2listw(LWard_knn, style="C",zero.policy=TRUE)
```

#Run Moran's I using the residuals from our final model
#first using queens neighbours
```{r warning=FALSE}

moran.test(ObesityMAP@data$`Model.residuals`, Lward.queens_weight,zero.policy=TRUE)
```

#Then knn = 4
```{r warning=FALSE}
moran.test(ObesityMAP@data$`Model.residuals`, Lward.knn_4_weight,zero.policy=TRUE)
```

##GWR(Andy MacLachlan and Adam Dennett,2019)
```{r warning=FALSE}
#calculate kernel bandwidth
GWRbandwidth <- gwr.sel(root_ob ~	`Percentage of Mixed children`+	`Percentage of Asian children`+	`Percentage of African children`+	`IMD education average score`+	`IMD health average score` +	`IMD IDACI average score`,data = modeldata,coords=coordsW,adapt=T)

#run the gwr model
gwr.model = gwr(root_ob ~	`Percentage of Mixed children`+	`Percentage of Asian children`+	`Percentage of African children`+	`IMD education average score`+	`IMD health average score` +	`IMD IDACI average score`,data = modeldata,coords=coordsW, adapt=GWRbandwidth, hatmatrix=TRUE, se.fit=TRUE)

#print the results of the model
gwr.model
```

#Attach coefficients to original dataframe
```{r warning=FALSE}
results<-as.data.frame(gwr.model$SDF)
names(results)
ObesityMAP@data$coefr2<-results$localR2
ObesityMAP@data$coefmixed<-results$X.Percentage.of.Mixed.children.
ObesityMAP@data$coefafrican<-results$X.Percentage.of.African.children.
ObesityMAP@data$coefedu<-results$X.IMD.education.average.score.
ObesityMAP@data$coefhealth<-results$X.IMD.health.average.score.
ObesityMAP@data$coefasian<-results$X.Percentage.of.Asian.children.
ObesityMAP@data$coefidaci<-results$X.IMD.IDACI.average.score.

```
## Maps
#Local R-squared
```{r warning=FALSE}
tmap_mode("view")
tm_shape(ObesityMAP) +
  tm_polygons(col = "coefr2", title = "Local R-squared", breaks = c(-Inf,0.7,0.75,0.8,0.85,0.9,0.95, Inf), palette = "YlGnBu", alpha = 1)+
  tm_format_World(title = NA,legend.width = 0.8, scale = 1,
                  legend.position = c("left", "top"))+tm_scale_bar()+tm_compass()
```
```{r warning=FALSE}
tmap_mode("view")
tm_shape(ObesityMAP) +
  tm_polygons(col = "coefafrican", title = "Coefficient for percentage of African children", palette = "RdBu", alpha = 1)+
  tm_format_World(title = NA,legend.width = 0.8, scale = 1,
                  legend.position = c("left", "top"))+tm_scale_bar()+tm_compass()
```

#Percentage of mixed children
```{r warning=FALSE}
tm_shape(ObesityMAP) +
  tm_polygons(col = "coefmixed", title = "Coefficient for percentage of Mixed children",breaks = c(-Inf,-20,-10,-5,0,5,10,15, Inf),  palette = "RdBu", alpha = 1)+
  tm_format_World(title = NA,legend.width = 0.8, scale = 1,
                legend.position = c("left", "top"))+tm_scale_bar()+tm_compass()
```

#Percentage of Asian children
```{r warning=FALSE}
tm_shape(ObesityMAP) +
  tm_polygons(col = "coefasian", title = "Coefficient for percentage of Asian children",  palette = "RdBu", alpha = 1)+
  tm_format_World(title = NA,legend.width = 0.8, scale = 1,
                legend.position = c("left", "top"))+tm_scale_bar()+tm_compass()
```

#IDACI score
```{r warning=FALSE}
tm_shape(ObesityMAP) +
  tm_polygons(col = "coefidaci", title = "Coefficient for IMD IDACI average acore", breaks = c(-Inf,-2,0,2,4,6,8, Inf), palette = "RdBu", alpha = 1)+
  tm_format_World(title = NA,legend.width = 0.8, scale = 1,
                  legend.position = c("left", "top"))+tm_scale_bar()+tm_compass()
```

#IMD Health score
```{r warning=FALSE}
tm_shape(ObesityMAP) +
  tm_polygons(col = "coefhealth", title = "Coefficient for IMD Health average acore",  palette = "RdBu", alpha = 1)+
  tm_format_World(title = NA,legend.width = 0.8, scale = 1,
                  legend.position = c("left", "top"))+tm_scale_bar()+tm_compass()
```

#IMD education
```{r warning=FALSE}
tm_shape(ObesityMAP) +
  tm_polygons(col = "coefedu", title = "Coefficient for IMD Education average acore", palette = "RdBu", alpha = 1)+
  tm_format_World(title = NA,legend.width = 0.8, scale = 1,
                  legend.position = c("left", "top"))+tm_scale_bar()+tm_compass()
```


## SECTION 3: Cluster analysis
```{r warning=FALSE}
#render("Report code.Rmd", output_dir = output_dir, params = list(output_dir = output_dir))
modeldata2<- childdata2[,c("GSS_CODE","root_ob","Percentage of Mixed children","Percentage of Asian children","Percentage of African children",
"IMD education average score","IMD health average score","IMD IDACI average score")]
```
Cluster analysis(Guy Lansley and James Cheshire,2018)
```{r warning=FALSE,message=FALSE}
clusterdata<- childdata2[,c("root_ob","Percentage of Mixed children","Percentage of Asian children","Percentage of African children",
"IMD education average score","IMD health average score","IMD IDACI average score")]
value <- colnames(clusterdata)
# creates a new data frame
stand_data <- clusterdata
for(i in 1: ncol (clusterdata)){
stand_data[, value[i]] <- scale(as.numeric(modeldata2[, value[i]]))
}


```

#K-means clustering (k=5)
```{r warning=FALSE}

Km <- kmeans(stand_data, 5, nstart = 25, iter.max = 1000)
KmClusters <- as.matrix(Km$cluster)
KmClusters <- as.data.frame(KmClusters)
KmCenters <- as.matrix(Km$centers)
KmCenters <- as.data.frame(KmCenters)
#Number of LAs in each cluster
table(KmClusters)
```

#Validate choice of k
```{r warning=FALSE}
# Total within-cluster sum of square
wss <- NULL
for (i in 1:15) wss[i] <- kmeans(stand_data,centers = i,iter.max = 1000)$tot.withinss
plot(1:15, wss, type = "b", pch = 19, xlab = "Number of Clusters",
ylab = "Total within-cluster sum of squares")
```



#Cluster plot of the first 2 principal components
```{r warning=FALSE}
library(cluster)
clusplot(stand_data,Km$cluster, color = TRUE, shade = FALSE,
labels = 4, lines = 0, plotchar = FALSE)
```
```{r warning=FALSE}
#More cluster plot
library(ggplot2)
library(factoextra)
fviz_cluster(Km, data = stand_data, geom = "point", ellipse = F, pointsize = 0.5,
ggtheme = theme_classic())
```


#Radial plot for each group

```{r warning=FALSE}
library(plotrix)
KmCenters[5,]<- c(0)
par(cex.axis = 0.8, cex.lab = 0.8)
radial.plot(KmCenters[c(1,5),], labels = colnames(KmCenters),
boxed.radial = FALSE, show.radial.grid = TRUE,
line.col = c("blue", "red"), radlab = TRUE,
rp.type = "p", show.grid.labels = 3)
```
##Creates a map of cluster groups
```{r warning=FALSE}
#Join the cluster labels to the GSS codes
GSScode<- childdata2[,c(1,2)]
Classification <- as.data.frame(cbind(as.character(GSScode[,1]), KmClusters[,1]))
names(Classification) <- c("GSS_CODE", "Classification")

OA.Class<- merge(ObesityMAP, Classification, by.x = "GSS_CODE", by.y = "GSS_CODE",duplicateGeoms = TRUE)

# creates a map in R
tm_shape(OA.Class) +
  tm_polygons(col = "Classification", title = "Cluster groups", palette = "RdBu", alpha = 1)+
  tm_format_World(title = NA,legend.width = 0.8, scale = 1,
                  legend.position = c("left", "top"))+tm_scale_bar()+tm_compass()
```

Reference:
Andy MacLachlan and Adam Dennett, 2019. CASA0005 Geographic Information Systems and Science. Available from: https://andrewmaclachlan.github.io/CASA0005repo/index.html

Guy Lansley and James Cheshire,2018.Creating a Geodemographic Classification Using K-means Clustering in R.Available from: https://data.cdrc.ac.uk/tutorial/creating-a-geodemographic-classification-using-k-means-clustering-in-r

